Software Citation Principles

### 2016-07-20 sc-principles/rebuttal/rebuttal.tex

\textbf{Our response:}
Thank you for pointing this error out---we have corrected this statement to indicate that the past discussion led to a second version (what was submitted).

\item \textbf{Reviewer comment:}
\emph{line 97: ``the need for credit for application software underscores the need to overhaul the system of credit for all research products.'': Very true and very important. But then maybe the concept of a ``citation'' is obsolete altogether, and we shouldn't be advocating ``software citations'', but something new altogether? Some more discussion on this would be valuable, I think. This relates to my comment above about a long-term vision.}

\textbf{Our response:}
\asnote{We probably need to dig out some citations about improved/rich citation. I'm aware of some work that was going on in the PLOS Labs group about this but I'm not sure if that work was ever published.}

\niemnote{The idea of citations is not going to go away---but format and how they fit in ecosystem may change.}

@@

\textbf{Our response:}

\begin{enumerate}[label={(\alph*)}]
\item Agreed for 1 and 2.
\item \niemnote{I think I agree, or at least benefit}
\item \niemnote{I think what we had originally makes sense, but perhaps there needs to be more explanation?}
\item \niemnote{no, indexed citations not really relevant for catalog/registry, unless it wants to display citations of software---but that is use case 4}
\item \niemnote{no, I don't think those things would be stored---because they aren't included in the citation itself}
\item We intended ``find'' to mean more than discovery, but since the appendix was not present in the first submission this was not clear. We have altered the use case to be ``Find/choose software to implement task'' to make it clear that this use case goes beyond discovery.
\end{enumerate}

\katznote{also as a general comment, see the new intro to appendix B that states that some of this may be incomplete or wrong, but is included as a record to support the process that come up with the body of the document, and that Appendix B will be subject to further work in the future.}

### 2016-07-20 sc-principles/software-citation-principles.tex
adding description for B.10 and in google doc
adding some sentences to the start of B and a note in the rebuttal to refer to this

This appendix records an edited, extended description of the use cases discussed in~\S\ref{sec:use_cases}, originally found in~\cite{SC-Use-Cases}.

@@

>>>>

This appendix records an edited, extended description of the use cases discussed in~\S\ref{sec:use_cases}, originally found in~\cite{SC-Use-Cases}.  This discussion
is not fully complete, and in some cases, it may not be fully self-consistent, but it is
part of this paper as a record of one of the inputs to the principles.  We expect that
the follow-up Software Citation Implementation Group will further develop these uses
case, including explaining in more detail how the software citation principles can be applied
to each as part of working with the stakeholders to persuade them to actually implement
the principles in their standard workflows.

@@

This case asks what information regarding software is needed for a publisher who wants to publish papers that cite that software.
